---
title:  Life History Repository 
output:
  html_document:
    theme: cerulean
    toc: true
    toc_float: true
    collapsed: false
    smooth_scroll: false
    number_sections: false
#runtime: shiny
---


```{css, echo=FALSE}

body {
  padding: 0;
  margin: 0;
  font-family: "Open Sans", "Helvetica Neue", Helvetica, Arial, sans-serif;
  font-size: 16px;
  line-height: 1.5;
}

h1.title {
  font-size: 3.5em;
}


table th {
  font-weight: bold;
  background-color: #2fa4e7;
  color: #f0f6fa;
}

table tr:nth-child(odd) {
      background-color: #f0f6fa;
}


```



```{r, include=FALSE, echo=FALSE}

# library(RWordPress)
# options(WordpressLogin = c(pamoore = 'FishIsABish2021!'),
#         WordpressURL = 'https://natureanalytics.ca/xmlrpc.php')
# library(knitr)
# knit2wp('lh_repository.Rmd',
#         title = 'Life History Repository', 
#         action = c("newPage"),
#         publish = TRUE)


library(fishSimGTG)
library(dplyr)
library(here)
library(kableExtra)
library(prettydoc)
library(aws.s3)
library(tidyverse)
library(htmltools)

space_info<- function(prefix = NULL, 
                      fileExt = "rds",
                      bucket = Sys.getenv("SPACES_BUCKET")) {
  
  bucket <- as.character(unlist(stringr::str_split(bucket, "/", 2))[1])
  
  if(!is.null(prefix)) prefix <- as.character(paste0(prefix,"/"))
  
  #Returns NULL if cannot communicate with server
  show_condition <- function(code) {
    tryCatch(code,
             condition = function(c) {
               NULL
             }
    )
  }
  
  space_info<-show_condition(aws.s3::get_bucket_df(
                                      bucket =  bucket,
                                      prefix = prefix,
                                      region = Sys.getenv("SPACES_REGION"),
                                      check_region = FALSE,
                                      key = Sys.getenv("SPACES_ACCESS_KEY"),
                                      secret = Sys.getenv("SPACES_SECRET_KEY"),
                                      base_url = Sys.getenv("SPACES_BASE"),
                                      max = Inf))
  #-----------------------
  #Filter to only fileExt
  #----------------------
  if(!is.null(space_info)){
    fileExt = paste0(".", fileExt)
    end = -1*nchar(fileExt)-1
    space_info<-space_info %>% 
      filter(stringr::str_detect(Key, pattern = fileExt))  %>%
      mutate(Time = stringr::str_subset(stringr::str_split(LastModified, "T", simplify=TRUE), "Z")) %>%
      mutate(Date = as.Date(LastModified)) %>%
      mutate(ProjectName = stringr::str_sub(stringr::str_subset(stringr::str_split(Key, "/", simplify=TRUE), fileExt), end=end))
    
  }
  return(space_info)
}


space_getRDS<- function(object,
                        bucket = Sys.getenv("SPACES_BUCKET")) {
  
  object <- as.character(object)
  bucket <- as.character(bucket)
  
  #Returns NULL if cannot communicate with server
  show_condition <- function(code) {
    tryCatch(code,
             condition = function(c) {
               NULL
             }
    )
  }
  output<-show_condition(
    aws.s3::s3readRDS(object=object,
                      bucket=bucket,
                      region = Sys.getenv("SPACES_REGION"),
                      check_region = FALSE,
                      key = Sys.getenv("SPACES_ACCESS_KEY"),
                      secret = Sys.getenv("SPACES_SECRET_KEY"),
                      base_url = Sys.getenv("SPACES_BASE"))
  )
  
  return(output)
}


```

```{r, echo=FALSE}

grabber <-  lapply(
  X = sort(space_info()$Key), 
  FUN = function(X){
    space_getRDS(X)
                   })

runReport<-NROW(grabber) > 0
```

```{r, eval = runReport, echo = FALSE}

namesGrabber<- unlist(lapply(
    X = 1:NROW(grabber), function(X){
      grabber[[X]]@speciesName
    }
  ))

src <- lapply(
  X = order(namesGrabber),
  FUN = function(X) {
    knitr::knit_expand(
      file = here::here("child", "template2.Rmd"),
      x = X
    )
  }
)

#print(unlist(src))
```


# About

This repository contains life history information for species of fish, as entered by users of TNC Size Limit application. These life histories can be used to estimate spawning potential ratio and fishing yield-per-recruit for alternative size limit regulations. 

# Explore Life Histories

`r #knitr::knit(text = unlist(src))`

`r if(runReport){
knitr::knit(text = unlist(src))
}`




 
